---
title: 'HW4: Problem 2'
author: "jgn2108"
date: "`r Sys.Date()`"
output: html_document
---
#Libraries
```{r}
library(tidyverse)
library(httr)
library(jsonlite)
```

#retrieve the data from the provided URL: DOHMH New York City Restaurant Inspection Results
```{r}
get_all_inspections <- function(url) {
  
  all_inspections <- vector("list", length = 0)
  
  loop_index <- 1
  chunk_size <- 50000
  DO_NEXT <- TRUE
  
  while (DO_NEXT) {
    message("Getting data, page ", loop_index)
    
    all_inspections[[loop_index]] <- 
      GET(url,
          query = list(`$order` = "zipcode",
                       `$limit` = chunk_size,
                       `$offset` = as.integer((loop_index - 1) * chunk_size)
          )
      ) %>%
      content("text") %>%
      fromJSON() %>%
      as_tibble()
    
    DO_NEXT <- dim(all_inspections[[loop_index]])[1] == chunk_size
    loop_index <- loop_index + 1
  }
  
  bind_rows(all_inspections)
}

url <- "https://data.cityofnewyork.us/resource/43nn-pn8j.json"

nyc_inspections <- get_all_inspections(url)

```

```{r}
# Display column names
col_names <- names(nyc_inspections)
col_names
```

#Remove rows with missing observations (nyc_inspections_filtered)
```{r}
# Remove rows with missing observations
nyc_inspections_filtered <- na.omit(nyc_inspections) #from 209,222 observations filtered down to 91,260

```

#Now look at data for zipcode 10009
```{r}
library(dplyr)

# Filter data for the specific zipcode (e.g., 10009)
nyc_inspections_zipcode <- nyc_inspections %>%
  filter(zipcode == 10009)

```

#remove 10009 data with missing observations
```{r}
library(tidyr)

# Filter out rows with missing data
nyc_inspections_zipcode_clean <- drop_na(nyc_inspections_zipcode) #from 2283 observations to 943 observations

```

#now combine building variable with street variable to get the address of the restaurants
```{r}
# Create a new variable "address" by combining "building" and "street"
nyc_inspections_zipcode_clean <- nyc_inspections_zipcode_clean %>%
  mutate(address = paste(building, street, sep = " "))

# View the updated df
head(nyc_inspections_zipcode_clean)

```
#convert tiblle into a normal df
```{r}
# Convert tibble to data frame
nyc_inspections_zipcode_clean_df <- as.data.frame(nyc_inspections_zipcode_clean)

# View the resulting data frame
head(nyc_inspections_zipcode_clean_df)

```

#load libraries I will need for these fancy plots
```{r}
#install.packages("plotly")
library(tidyverse)
library(plotly)
library(dplyr)
```
#scatter plot like the lecture
```{r}
# Create the scatter plot
nyc_inspections_zipcode_clean_df %>%
  plot_ly(
    x = ~latitude, 
    y = ~longitude, 
    type = "scatter", 
    mode = "markers",
    color = ~grade,  # Assuming "grade" is a categorical variable
    text = ~paste("Grade: ", grade),
    alpha = 0.5
  ) %>%
  layout(
    title = "NYC Restaurant Inspection Grades",
    xaxis = list(title = "Latitude"),
    yaxis = list(title = "Longitude")
  )
```

#That plot is gross...lets try grade vs. street
```{r}
plot_ly(
  data = nyc_inspections_zipcode_clean_df,
  x = ~street,
  y = ~grade,
  type = "scatter",
  mode = "markers",
  text = ~paste("Grade: ", grade, "<br>Street: ", street),
  marker = list(size = 10, color = ~grade)
) %>%
  layout(title = "Grade vs Street",
         xaxis = list(title = "Street"),
         yaxis = list(title = "Grade"))
```

#googled how to add color to grades
```{r}
plot_ly(
  data = nyc_inspections_zipcode_clean_df,
  x = ~street,
  y = ~grade,
  type = "scatter",
  mode = "markers",
  text = ~paste("Grade: ", grade, "<br>Street: ", street),
  color = ~grade,
  colors = c("A" = "green", "B" = "blue", "C" = "orange", "P" = "purple", "Z" = "red"),
  marker = list(size = 10)
) %>%
  layout(title = "Grade vs Street",
         xaxis = list(title = "Street"),
         yaxis = list(title = "Grade"))

```

#list all restuarant names and addressed if they have an A
```{r}
library(dplyr)
# Filter the data for grade A
grade_A_data <- nyc_inspections_zipcode_clean_df %>%
  filter(grade == "A")

# Create a table of restaurant names (dba), their locations (address),
# grade, and inspection date
restaurant_table <- grade_A_data %>%
  select(dba, address, grade, inspection_date)

# Arrange the table alphabetically by restaurant names
restaurant_table <- arrange(restaurant_table, dba)

# Print the sorted table
print(restaurant_table)

```
#Attempt a Plotly boxplot
```{r}
# mutate to reorder "street" based on the median grade
nyc_inspections_zipcode_clean_df <- nyc_inspections_zipcode_clean_df %>%
  mutate(street = fct_reorder(street, grade, .fun = median))

# Create a Plotly boxplot for "grade" by "street"
boxplot <- nyc_inspections_zipcode_clean_df %>%
  plot_ly(y = ~grade, color = ~street, type = "box", colors = "viridis")

# Show the plot
boxplot
```
This boxplot was more informative than the scatterplot

#bar chart of number of places in zipcode 10009 with restaurants in each category
```{r}
# Count the occurrences of each grade
grade_counts <- nyc_inspections_zipcode_clean_df %>%
  count(grade)

# Create a Plotly barchart
barchart <- grade_counts %>%
  plot_ly(x = ~grade, y = ~n, type = "bar", marker = list(color = "skyblue"))

# Show the barchart
barchart
```
The bar chart is the most informative - showing me taht in my neighborhood, a small proportion of restaurants have inspection grades less than an A. Comforting.
